MacLeish

### 2016-04-07 README.Rmd
moved to GitHub README

---
title: "MacLeish"
output:
  html_document:
    keep_md: true
---

@@

```{r, fig.width=7, fig.height=7, message=FALSE}
library(leaflet)
leaflet() %>%
  addTiles() %>%
  addPolygons(data = macleish_layers[["boundary"]], 
              weight = 1, fillOpacity = 0.1) %>%
  addPolygons(data = macleish_layers[["buildings"]], 
              weight = 1, popup = ~ Feature) %>%
  addPolylines(data = macleish_layers[["trails"]], 
               weight = 1, color = "brown",
               popup = ~ trl_name) %>%
  addPolylines(data = macleish_layers[["streams"]], 
               weight = 2)
```

>>>>

---
title: "MacLeish"
output:
  github_document:
    html_preview: true
---

@@

```{r, eval=FALSE, fig.width=7, fig.height=7, message=FALSE}
library(leaflet)
leaflet() %>%
  addTiles() %>%
  addPolygons(data = macleish_layers[["boundary"]], 
              weight = 1, fillOpacity = 0.1) %>%
  addPolygons(data = macleish_layers[["buildings"]], 
              weight = 1, popup = ~ Feature) %>%
  addPolylines(data = macleish_layers[["trails"]], 
               weight = 1, color = "brown",
               popup = ~ trl_name) %>%
  addPolylines(data = macleish_layers[["streams"]], 
               weight = 2)
```
